Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-03-25 src/tex/ms.tex
mention winds

\rev{
Planets around M~dwarfs, in particular, may be subject to significant atmospheric loss due to the extended high-luminosity pre-main-sequence phase of their host stars~\citep[e.g.,][]{Luger2015}.
%During this period, extreme X-ray and UV irradiation can drive rapid hydrodynamic escape, potentially stripping a planet of its primordial atmosphere before abiogenesis can occur.
%Even after this early phase, M-dwarf planets remain exposed to intense stellar activity, leading to further erosion of secondary atmospheres if not replenished through volcanic outgassing or other mechanisms.
Recent works~\citep[e.g.,][]{Coy2024,Luque2024} interpret JWST eclipse measurements as growing evidence for the absence of substantial atmospheres on M-dwarf rocky exoplanets.
If these planets indeed lack atmospheres, their habitability would be primarily dictated by the rate of atmospheric escape~\citep[e.g.,][]{Owen2020}.
However, alternative interpretations remain viable: \citet{Ducrot2024} and \citet{Hammond2025} recently demonstrated that current JWST data cannot definitively distinguish between a bare-rock scenario and an atmosphere composed primarily of N$_2$-CO$_2$-H$_2$O.
This underscores the need for future observations and modeling efforts to constrain atmospheric retention and escape processes more robustly.}
%For instance, atmospheric escape processes may play a critical role not only in maintaining a planet's atmosphere but also in regulating the planet's water inventory and the availability of volatile elements for prebiotic chemistry.

>>>>

\rev{
Planets around M~dwarfs, in particular, may be subject to significant atmospheric loss due to the extended high-luminosity pre-main-sequence phase of their host stars}\revv{, and stellar winds can play a major role in stripping secondary atmospheres ~\citep[e.g.,][]{Luger2015,Dong2018,Garcia-Sage2017}.
Recent works~\citep[e.g.,][]{Coy2024,Luque2024} interpret JWST eclipse measurements as growing evidence for the absence of substantial atmospheres on M-dwarf rocky exoplanets.
If these planets indeed lack atmospheres, their habitability would be primarily dictated by the rate of atmospheric escape~\citep[e.g.,][]{Owen2020}.
However, alternative interpretations remain viable: \citet{Ducrot2024} and \citet{Hammond2025} recently demonstrated that current JWST data cannot definitively distinguish between a bare-rock scenario and an atmosphere composed primarily of N$_2$-CO$_2$-H$_2$O.
This underscores the need for future observations and modeling efforts to constrain atmospheric retention and escape processes more robustly.}
%For instance, atmospheric escape processes may play a critical role not only in maintaining a planet's atmosphere but also in regulating the planet's water inventory and the availability of volatile elements for prebiotic chemistry.
